lab-meeting

### 2018-02-25 Report/lab-meeting.Rmd
Updates presentation

@@

```{r, echo = T}
walk_all %>% 
  group_by(condition) %>% 
  summarise(p.value = t.test(distance ~ phase)$p.value,
            phase1 = t.test(distance ~ phase)$estimate[[1]],
            phase2 = t.test(distance ~ phase)$estimate[[2]])
```

## Time

>>>>

XXX example image

@@

```{r, echo = F,results='hide'}
walk_all %>% 
  group_by(condition) %>% 
  summarise(p.value = t.test(distance ~ phase)$p.value,
            phase1 = t.test(distance ~ phase)$estimate[[1]],
            phase2 = t.test(distance ~ phase)$estimate[[2]])
```
```{r, echo = T}
aov_distance_condition <- aov(min_norm_distance~condition*phase, 
                              data = walk_all)
summary(aov_distance_condition)
```
```{r, echo = T}
aov_distance_condition_2 <- aov(min_norm_distance~condition, 
                              data = walk_all[walk_all$phase == 2,])
summary(aov_distance_condition_2)
```
## Time

Time absolute
```{r, echo = F,warning=FALSE}
ggplot(walk_all, aes(x = condition, y = time, fill=factor(phase))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95),geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

Time normalised
```{r, echo = F,warning=FALSE}
ggplot(walk_all, aes(x = condition, y = min_norm_time, fill=factor(phase))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95),geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

```{r, echo = F,results='hide'}
walk_all %>% 
  group_by(condition) %>% 
  summarise(p.value = t.test(time ~ phase)$p.value,
            phase1 = t.test(time ~ phase)$estimate[[1]],
            phase2 = t.test(time ~ phase)$estimate[[2]])
```
```{r, echo = T}
aov_time_condition <- aov(min_norm_time~condition*phase, 
                              data = walk_all)
summary(aov_time_condition)
```
```{r, echo = T}
aov_time_condition_2 <- aov(min_norm_time~condition, 
                              data = walk_all[walk_all$phase == 2,])
summary(aov_time_condition_2)
```

## Pointing accuracy

```{r, echo = F,warning=FALSE}
ggplot(sop_all, aes(x = condition, y = abs(error), fill=factor(phase))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95),geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```

```{r, echo = T}
aov_point_condition <- aov(abs(error)~condition*phase, 
                           data = sop_all)
summary(aov_point_condition)
```

```{r, echo = T}
aov_point_condition_2 <- aov(abs(error)~condition, 
                             data = sop_all[sop_all$phase == 2, ])
summary(aov_point_condition_2)
```
